How predictable is extinction?

### 2018-12-20 doc/methods.tex
added in taxon figures. filled out basic captions
full set of cv figures for all datasets

We analyzed microfossil occurrence information which was downloaded from the Neptune Database \url{http://www.nsb-mfn-berlin.de/nannotax}. We downloaded all occurrence information for calcareous nannofossils, diatoms, foraminifera, and radiolarians from the entire globe and having occurred between 120 and 0 Mya. This selection of occurrences was then culled to just those species which have their first occurrence at most 63 My; this avoids those taxa which survived the K/Pg boundary, those taxa arising just after the K/Pg boundary, and lines up the occurrences with the temperature time-series (discussed below).

All occurrences were binned into 1 My bins based on the estimated age of the fossil occurrence. Because the estimated ages of each occurrence is a product of core-specific age-models and can be overly precise, the hope is that by binning the data this smooths over the between-core heterogeneity and thus homogenizes our disparate data sources. We then determined for each species the million year bins when it had occurred. For every occurrence of a species, except the last, that species is considered to have survived and was marked with a 0. The last occurrence of that species is considered the bin in which the taxon has gone extinct. This protocol means that we are reading the fossil record ``as written,'' a practice that is potentially dangerous as it is a overconfident statement of preservation and may be shortening the actual duration of that species CITATIONS. However, this practice is common with marine microfossil data CITATIONS.

@@

\section{Model Selection and Adequacy}

>>>>

We analyzed microfossil occurrence information which was downloaded from the Neptune Database \url{http://www.nsb-mfn-berlin.de/nannotax}. All occurrence information was downloaded for calcareous nannofossils, diatoms, foraminifera, and radiolarians -- these occurrences span the entire globe between 120 and 0 million years ago (Mya). This dataset of occurrences was then filtered to just those species which have their first occurrence at most 63 Mya. This choice means that our analysis avoids those taxa which survived the K/Pg boundary, those taxa which arose just after the K/Pg boundary, and means that our occurrence histories line up with the temperature time-series which was used as a predictor of extinction (discussed below).

All fossil occurrences were assigned to 1 My bins based on the estimated age of the fossil occurrence. Because the estimated ages of each occurrence is a product of core-specific age-models and can be overly precise, the hope is that by binning the data this smooths over the between-core heterogeneity and thus homogenizes our disparate data sources. The occurrence histories of each species were then given binary codes used to model the presence or extinction of those species. For every occurrence of a species, except the last, that species is considered to have survived and was marked with a 0. The last occurrence of that species is considered the bin in which the taxon has gone extinct -- and is assigned a 1. This protocol means that we are reading the fossil record ``as written,'' a practice that is potentially dangerous as it is a overconfident statement of preservation and may be shortening the actual duration of that species CITATIONS. However, this practice is common with marine microfossil data CITATIONS. In fact, with marine microfossils collected from cores a bigger problem may be over extending the duration of a species due to mixing and smearing within the cores CITATIONS.

@@

\section{Model adequacy}
